\documentclass[UTF8,12pt,a4paper]{ctexart}

\usepackage{geometry}
\geometry{left=2.6cm,right=2.6cm,top=2.5cm,bottom=2.5cm}
\usepackage{setspace}
\setstretch{1.4}
\usepackage{amsmath,amssymb,bm}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{algpseudocode}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\title{基于TCGA-BRCA多组学融合的乳腺癌分子亚型分类研究}
\author{YuYe10\quad Cancer-Classification Project}
\date{2026年4月}

\begin{document}

\maketitle

\newpage

% 中文摘要独立成页
\begin{abstract}
\textbf{中文摘要：}乳腺癌分子亚型的精准识别对个体化治疗具有重要临床意义。本研究基于TCGA-BRCA数据库的RNA-seq转录组、DNA甲基化及PAM50标签数据，系统比较了RNA单模态、早期融合（Concat）、潜在因子融合（MOFA）与堆叠集成（Stacking）四种策略的亚型分类性能。研究构建了严格的防泄露评估框架：所有特征筛选、标准化、MOFA拟合及Stacking元特征构造均限定在训练折内完成，测试折仅用于独立推断。主实验采用重复分层5折交叉验证（$n=50$测试折），以Accuracy、Balanced Accuracy和Macro-F1为核心指标，报告95\%置信区间。

实验结果表明，在约150例有效样本的三分类任务中，Concat-SVM取得最优性能（Accuracy=90.64\%，Macro-F1=90.03\%），MOFA-20因子次之（Accuracy=90.00\%），两者差距不足1个百分点。RNA单模态基线已达89.78\%，表明转录组数据蕴含丰富的亚型判别信息。Stacking策略表现令人意外：被设计为"SOTA"的XGB+XGB配置仅获78.66\% Macro-F1，所有Stacking变体均显著低于简单融合基线（$p<0.05$），提示在小样本高维条件下增加融合层级反而引入过拟合风险。补充实验涵盖特征维度敏感性（100--1500维）、CV参数敏感性及消融实验等41组配置。本研究建立了可审计、可复现的多组学融合评估框架，并系统揭示了"简单方法优于复杂方法"的反直觉现象。

\vspace{0.5em}
\noindent\textbf{关键词：}多组学融合；乳腺癌；分子亚型分类；MOFA；Stacking；防泄露交叉验证
\end{abstract}

\newpage

% 英文摘要独立成页
\begin{abstract}
\textbf{Abstract:} Accurate molecular subtyping of breast cancer is essential for personalized therapeutic decisions. This study systematically evaluates four fusion strategies---RNA-only baseline, early fusion (Concat), latent factor fusion (MOFA), and stacked ensemble (Stacking)---for PAM50 molecular subtyping using RNA-seq transcriptomics, DNA methylation, and clinical labels from the TCGA-BRCA cohort. We established a strict anti-leakage evaluation framework where all feature selection, standardization, MOFA factor fitting, and Stacking meta-feature construction are confined within training folds. The primary experiments employ repeated stratified 5-fold cross-validation ($n=50$ test folds), reporting Accuracy, Balanced Accuracy, and Macro-F1 with 95\% confidence intervals.

Results on approximately 150 effective samples (three-class: LumA/LumB/Basal) demonstrate that Concat-SVM achieves optimal performance (Accuracy=90.64\%, Macro-F1=90.03\%), followed closely by MOFA with 20 factors (Accuracy=90.00\%), with less than 1\% gap between them. The RNA-only baseline reaches 89.78\% Accuracy, indicating that transcriptomic data alone carries substantial subtype-discriminative information. Surprisingly, Stacking ensembles underperform significantly: the purported "SOTA" XGB+XGB configuration attains only 78.66\% Macro-F1, and all Stacking variants lag behind simple fusion baselines ($p<0.05$), suggesting that additional fusion layers introduce overfitting risks under small-sample high-dimensional conditions. Complementary sensitivity analyses spanning feature dimensions (100--1500), CV parameters, and ablation studies comprise 41 experimental configurations. This work establishes an auditable and reproducible multi-omics fusion evaluation framework, and systematically reveals the counter-intuitive phenomenon that simpler methods outperform complex ones on this dataset.

\vspace{0.5em}
\noindent\textbf{Keywords:} multi-omics fusion; breast cancer; molecular subtyping; MOFA; Stacking; anti-leakage cross-validation
\end{abstract}

\newpage

\tableofcontents
\newpage

\input{sections/01-background}
\input{sections/07-related-work}
\input{sections/02-data}
\input{sections/03-method}
\input{sections/04-experiments}
\input{sections/04-results-statistical-framework}
\input{sections/09-results-visualization}
\input{sections/10-discussion}
\input{sections/05-conclusion}
\input{sections/11-references}

\end{document}
