\section{参考文献}

本文采用顺序编码与手工条目方式列出参考文献，便于在不额外引入 bib 文件的情况下直接编译。

\begin{thebibliography}{99}

\bibitem{tcga2013}
The Cancer Genome Atlas Network.
Comprehensive molecular portraits of human breast tumours.
\emph{Nature}, 2012, 490(7418): 61--70.

\bibitem{xena2017}
Goldman M J, Craft B, Swatloski T, et al.
The UCSC Xena platform for public and private cancer genomics data visualization and interpretation.
\emph{BioRxiv}, 2018.

\bibitem{pam50}
Parker J S, Mullins M, Cheang M C U, et al.
Supervised risk predictor of breast cancer based on intrinsic subtypes.
\emph{Journal of Clinical Oncology}, 2009, 27(8): 1160--1167.

\bibitem{mofa2016}
Argelaguet R, Velten B, Arnol D, et al.
Multi-Omics Factor Analysis—a framework for unsupervised integration of multi-omics data sets.
\emph{Molecular Systems Biology}, 2018, 14(6): e8124.

\bibitem{svm1995}
Cortes C, Vapnik V.
Support-vector networks.
\emph{Machine Learning}, 1995, 20: 273--297.

\bibitem{shap2017}
Lundberg S M, Lee S-I.
A unified approach to interpreting model predictions.
\emph{Advances in Neural Information Processing Systems}, 2017.

\bibitem{mogonet2021}
Wang T, et al.
MOGONET integrates multi-omics data using graph convolutional networks for biomedical classification.
\emph{Briefings in Bioinformatics}, 2021.

\bibitem{aebersold2018}
Aebersold R, Mann M.
Mass-spectrometric exploration of proteome structure and function.
\emph{Nature}, 2016, 537: 347--355.

\bibitem{cawley2010}
Cawley G C, Talbot N L C.
On over-fitting in model selection and subsequent selection bias in performance evaluation.
\emph{Journal of Machine Learning Research}, 2010, 11: 2079--2107.

\bibitem{hughes1968}
Hughes G.
On the mean accuracy of statistical pattern recognizers.
\emph{IEEE Transactions on Information Theory}, 1968, 14(1): 55--63.

\end{thebibliography}
